PWNCAT2

### 2012-01-27 pwncatalog/PWNCAT2/paper/sections/analysis_of_the_fermi_lat_data.tex
update indent

Analysis goes here\ldots

>>>>

Methods for data analysis
\begin{itemize}
\item Cut on pulsar phase
\item Perform localization or extension fitting using \gtlike using energies from 1 \gev to 316 \gev.
\item Perform spectral analysis using \gtlike for energies above 100 \mev to 316 \gev.
\item There is a detection if  $\ts>25$ in the point-like source hypothesis after fitting the position of the point-like source. 
\item Consider the source to be extended if $\tsext>16$. Similar to extended source search paper \todo{cite extended source search paper}.
\item Calculate \tscut for all energies.
\end{itemize}

When to consider the source a pulsar or PWN.
\begin{itemize}
  \item If extended, then it is a PWN (cannot be a pulsar)
  \item If it is significiant for E>10 \gev, it is a PWN (too hard to be a pulsar)
  \item Otherwise, if it has a cutoff, it is a Pulsar candidate
  \item For point-like emission that is not significantly cutoff, the emission  mechanism is uncertain.
\end{itemize}

### 2012-01-27 pwncatalog/PWNCAT2/paper/sections/off_peak_phase_selection.tex
update indent

Off-peak goes here\ldots

@@

@@

\begin{deluxetable}{lcccc}
  \tabletypesize{\scriptsize}
  \tablecaption{Observatories, off-pulse definitions and distances of the \todo[inline]{How many pulsars?} \lat-detected pulsars
  \label{tab:off_peak_phase_range}
  }
  \input{tables/off_peak_phase_range}
  \tablecomments{\todo[inline]{Put table comments}}
\end{deluxetable}

>>>>

@@

To study the off-peak emission of \lat-detected pulsars, we first
developed a new method for defining the off-peak emission.
The primary constraint for this method was that it was systematic,
computationally efficient and model independent, and that it correctly
removed the pulsed emission for already studied pulsars.

The method we developed required first representing the

@@

\begin{deluxetable}{lcccc}
  \tabletypesize{\scriptsize}
  \tablecaption{Timing Observatories, definition of the off-peak region, and pulsar distances.
  \label{tab:off_peak_phase_range}
  }
  \input{tables/off_peak_phase_range}
  \tablecomments{\todo[inline]{Put table comments}}
\end{deluxetable}
